### 2013-09-13 paper_draft.tex
fixed conflicts
the version and rebuttal sent back to plos1

\subsection*{Sharing genotypic information}
Currently users can upload their genotyping results from the companies \textit{23andMe}, \textit{deCODEme} and \textit{FamilyTreeDNA} via a web interface to the openSNP 
project. There is experimental support for uploading exomes in the VCF format \cite{Danecek01082011}, as \textit{23andMe} recently started exome sequencing for its customers. Due to space constraints, openSNP currently only stores the SNPs of the exome data sets.
The uploaded data is published under the Creative Commons Zero license, 
which -- in accordance with the Panton Principles \cite{10.1371/journal.pbio.1001195} -- 
allows a complete re-use of the data without any constraints.
Between the launch of openSNP on 09/27/2011 and 10/27/2012, 633 people have signed 
up with openSNP, and 270 genetic datasets have been made available. As of 10/27/2012, the openSNP database lists 215,546,685 genotypes which are distributed over 2,140,643 unique SNPs.
Figures \ref{Figure1_label} and \ref{Figure2_label} depict the increase in users and genotyping files since September 2011.

@@

%\subsection*{Survey issues}
%
%As the survey was taken online by voluntary participants and was mainly spread in the personal genetics community, the results do not reflect the general population, but over-represent those people most likely to be interested in a project such as openSNP: customers of DTC genetic testing companies and people with a high interest in biology. 
%
Here, we present openSNP, a crowdsourced resource that enables customers of DTC testing companies to share their genotypings with researchers and receive new annotations for their genetic variants. With the number of active users already present on openSNP, we have shown that customers of DTC companies are willing to share their data at no cost to researchers around the world and are willing to annotate their data with phenotypes.

>>>>

\subsection*{Sharing genotypic information}
Currently users can upload their genotyping results from the companies \textit{23andMe}, \textit{deCODEme} and \textit{FamilyTreeDNA} via a web interface to the openSNP 
project. There is experimental support for uploading exomes in the VCF format \cite{Danecek01082011}, as \textit{23andMe} recently started exome sequencing for its customers. Due to space constraints on the database level, openSNP currently only displays the SNPs of the exome data sets on the website but the whole VCF files can be downloaded.
The uploaded data is published under the Creative Commons Zero license, 
which -- in accordance with the Panton Principles \cite{10.1371/journal.pbio.1001195} -- 
allows a complete re-use of the data without any constraints.
Between the launch of openSNP on 09/27/2011 and 10/27/2012, 633 people have signed 
up with openSNP, and 270 genetic datasets have been made available. As of 10/27/2012, the openSNP database lists 215,546,685 genotypes which are distributed over 2,140,643 unique SNPs.
Figures \ref{Figure1_label} and \ref{Figure2_label} depict the increase in users and genotyping files since September 2011.

@@

%\subsection*{Survey issues}
%
%As the survey was taken online by voluntary participants and was mainly spread in the personal genetics community, the results do not reflect the general population, but over-represent those people most likely to be interested in a project such as openSNP: customers of DTC genetic testing companies and people with a high interest in biology. 
%
Here, we present openSNP, a crowdsourced resource that enables customers of DTC testing companies to share their genotypings with researchers and receive new annotations for their genetic variants. Through a of number of active users already present on openSNP, we have shown that at least some customers of DTC companies are willing to share their data at no cost to researchers around the world and are willing to annotate their data with phenotypes.
